Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2015-12-07 jss/article.tex
Changed cite to citep

The correction for multiple testing by default is set to false discovery rate (fdr), which is equivalent to Benjamini \& Hochberg correction, but can be changed to any of the usual corrections such as Bonferroni, Holm, Hochberg, Holm, or Benjamini \& Yekutieli \cite{Benjamini2003FDR}, or even disabled .

@@

%represent_enrichment<-function(enrichment, plot = "heatmap" , scale = "log", 
%                               low = "steelblue" , high ="white",
%                              nrow = 1,sample_name = "Sample",
%                               na.value = "grey"){
Finally, to facilitate visualization of results, \pkg{ACSNMineR} integrates a representation function based on \pkg{ggplot2} syntax \cite{ggplot2}. It allows representation of results from \code{enrichment} or \code{multisample_enrichment} with a limited number of parameters. For examples, two types of display are available: heat-map tiles or bars. For multiple samples using a barplot representation the number of rows used can be provided, all plots will be on the same row otherwise. For the heatmap, the color of the non-significant modules, and boundaries of the gradient for significant values can also be tuned.

>>>>

The correction for multiple testing by default is set to false discovery rate (fdr), which is equivalent to Benjamini \& Hochberg correction, but can be changed to any of the usual corrections such as Bonferroni, Holm, Hochberg, Holm, or Benjamini \& Yekutieli \citep{Benjamini2003FDR}, or even disabled .

@@

%represent_enrichment<-function(enrichment, plot = "heatmap" , scale = "log", 
%                               low = "steelblue" , high ="white",
%                              nrow = 1,sample_name = "Sample",
%                               na.value = "grey"){
Finally, to facilitate visualization of results, \pkg{ACSNMineR} integrates a representation function based on \pkg{ggplot2} syntax \citep{ggplot2}. It allows representation of results from \code{enrichment} or \code{multisample_enrichment} with a limited number of parameters. For examples, two types of display are available: heat-map tiles or bars. For multiple samples using a barplot representation the number of rows used can be provided, all plots will be on the same row otherwise. For the heatmap, the color of the non-significant modules, and boundaries of the gradient for significant values can also be tuned.
